---
title: "Model Card: Prediction of students exam performance"
date: '`r Sys.Date()`'
output: 
  html_document
params:
    board: !r pins::model_board
    name: Daniel Steck
    version: 1
---

```{r setup, include=FALSE}
library(tidyverse)
library(vetiver)
library(pins)
library(yardstick)
knitr::opts_chunk$set(echo = FALSE)
v <- vetiver_pin_read(model_board, "Prediction_of_exam_score_model_r", version = NULL)
#v_meta <- pin_meta(params$model_board, params$name)
theme_set(theme_light())
```

A [model card](https://doi.org/10.1145/3287560.3287596) provides brief, transparent, responsible reporting for a trained machine learning model.

## Model details

-   Developed by Daniel Steck
-   `r cli::pluralize("{v$description} using {ncol(v$prototype)} feature{?s}")`
-   This model was developed within the lecture Programming languages for Data Science.
    -   This models predicts the average performance of students in an exam based on various generic attributes. Target was to evaluate which attributes have an impact on the performance in exams.
    -   The following variables are used within the model:
        -   Gender
        -   Ethnic group
        -   The level of education from their parents
        -   If they have a reduced price for their lunch
        -   If they have participated in preparation course for their exams
-   The following steps are included in a workflow for the feature engineering/ data preprocessing:
    -   Removal of missing values
    -   One Hot Encoding for the categorical variables
    -   Removal of outliers
    -   Removal of correlated features in the model
-   Version `r v$metadata$version` of this model was published at `r v_meta$created`
-   Citation and/or license details for the model
-   If you have questions about this model, please contact [daniel.steck\@lorem-ipsum.de](mailto:daniel.steck@lorem-ipsum.de){.email}

## Intended use

-   The primary intended uses of this model are ...
-   The primary intended users of this model are ...
-   Some use cases are out of scope for this model, such as ...

## Important aspects/factors

-   Aspects or factors (demographic, environmental, technical) that are relevant to the context of this model are ...
-   In evaluating this model, we examined aspects such as ...

## Metrics

-   The metrics used to evaluate this model are: - Root Mean Squared Error (RMSE),

    ```         
    -   R Squared (RSQ), and

    -   Mean Absolute Error (MAE).
    ```

-   These metrics are chosen because they are the most common metrics for assessing the performance of regression models, and that they are well understood by the data science community.

## Training data & evaluation data

-   The training dataset for this model was ...

-   The training dataset for this model has the "prototype" or signature:

    ```{r}
    glimpse(v$prototype)
    ```

-   The evaluation dataset used in this model card is ...

-   We chose this evaluation data because ...

```{r}
## EVALUATION DATA:

data(Sacramento, package = "modeldata")

## consider using a package like skimr or DataExplorer for automated 
## presentation of evaluation data characteristics
```

## Quantitative analyses {.tabset}

```{r}
## compute predictions for your evaluation data
## load packages needed for prediction:
library(parsnip)
library(workflows)
preds <- augment(v, Sacramento)
```

### Overall model performance

```{r}
preds %>%
    metrics(price, .pred)
```

### Disaggregated model performance

```{r}
preds %>%
    group_by(type) %>%
    metrics(price, .pred)
```

### Visualize model performance

```{r, fig.height=3}
preds %>%
    ggplot(aes(price, .pred, color = type)) +
    geom_abline(slope = 1, lty = 2, color = "gray60", size = 1.2) +
    geom_point(alpha = 0.5, show.legend = FALSE) +
    facet_wrap(vars(type))
```

### Make a custom plot

```{r}
preds %>%
    mutate(.resid = price - .pred) %>%
    ggplot(aes(longitude, latitude, color = .resid)) +
    geom_point(alpha = 0.8) +
    scale_color_gradient2() +
    coord_fixed()
```

## Ethical considerations

-   We considered ...

## Caveats & recommendations

-   This model does ...
-   This model does not ...
-   We recommend ...
